### 2019-07-23 manuscript_clean.Rmd
VCV analysis supplement

---
bibliography: manuscript.bib
csl: systematic-biology.csl
site: "bookdown::bookdown_site"
output:
  bookdown::pdf_document2:
    toc: FALSE
indent: TRUE
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
---

@@

To model the evolutionary associations between individual tentillum and nematocyst characters and the ability to capture particular prey types in the diet, we ran a series of phylogenetic generalized linear models (R phytools::phyloglm) (Appendix 17). In addition, we ran a series of comparative analyses to address hypotheses of diet-tentillum relationships posed in the literature. To test for correlated evolution among binary characters, we used Pagel’s test [@pagel1994detecting]. To characterize and evaluate the relationship between continuous characters, we used phylogenetic generalized least squares regressions (PGLS) [@grafen1989phylogenetic]. To compare the evolution of continuous characters with categorical aspects of the diet, we carried out a phylogenetic logistic regression (R nlme::gls).

@@

![\label{figure5} Left - Subset phylogeny showing the mapped feeding guild regimes that were used to inform the OUwie analyses. Right - Grid showing the prey items consumed from which the feeding guild categories were derived. Diet data were obtained from the literature review in Appendix 10.](Figures_final/figure5.jpg)

@@

*Evolution of nematocyst shape* – Haploneme nematocyst evolution has been mainly driven by a single large shift towards elongation in Tendiculophora, which contains the majority of described siphonophore species. There is one secondary return to more oval, less elongated haplonemes in *Erenna*, but it doesn't reach the sphericity present in Cystonectae or Pyrostephidae (Fig. \@ref(figure10)). Heteroneme evolution presents a less radical evolutionary history, where Tendiculophora evolved more elongate heteronemes, but the difference between theirs and other siphonophores is much smaller than the variation in shape within Tendiculophora, bearing no phylogenetic signal. In this group, evolution of heteroneme shape has diverged in both directions, and there is no correlation with haploneme shape, which has remained fairly constant (elongation between 1.5 and 2.5).

@@

Data available from the Dryad Digital Repository: http://dx.doi.org/10.5061/dryad.[NNNN](http://dx.doi.org/10.5061/dryad.[NNNN])
(Temporarily, for pre-print purposes, the Supplementary Materials and Online Appendices are all available in https://github.com/dunnlab/tentilla_morph/Supplementary_materials)

@@

## Author contributions {-}

  Alejandro Damian-Serrano (Yale University)  collected specimens and morphological data, executed phylogenetic analyses (tree inference and character evolution), elaborated the figures, wrote and reviewed the manuscript.

  Steven H.D. Haddock (Monterey Bay Aquarium Research Institute) contributed by facilitating the access to the field and collection tools, directing the ROV and blue water diving operations in the field. He also contributed extensive knowledge of the biology and ecology of the organisms, and reviewed the manuscript. The Haddock Lab contributed by sequencing many of the species included in the phylogeny presented here.

  Casey W. Dunn (Yale University) contributed by collecting specimens, providing invaluable insights and mentoring, and by reviewing the manuscript. In addition, his graduate dissertation work produced many of the sequences used for our phylogenetic analysis.

>>>>

---
bibliography: manuscript.bib
csl: systematic-biology.csl
site: "bookdown::bookdown_site"
output:
  bookdown::pdf_document2:
    toc: FALSE
indent: TRUE
monofont: "Times New Roman"
fontsize: 12pt
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{setspace}
  - \doublespacing
---

@@

To model the evolutionary associations between individual tentillum and nematocyst characters and the ability to capture particular prey types in the diet, we ran a series of phylogenetic generalized linear models (R phylolm::phyloglm) (Appendix 17). In addition, we ran a series of comparative analyses to address hypotheses of diet-tentillum relationships posed in the literature. To test for correlated evolution among binary characters, we used Pagel’s test [@pagel1994detecting]. To characterize and evaluate the relationship between continuous characters, we used phylogenetic generalized least squares regressions (PGLS) [@grafen1989phylogenetic]. To compare the evolution of continuous characters with categorical aspects of the diet, we carried out a phylogenetic logistic regression (R nlme::gls).

@@

![\label{figure5} Left - Subset phylogeny showing the mapped feeding guild regimes that were used to inform the *OUwie* analyses. Right - Grid showing the prey items consumed from which the feeding guild categories were derived. Diet data were obtained from the literature review in Appendix 10.](Figures_final/figure5.jpg)

@@

*Evolution of nematocyst shape* – Haploneme nematocyst evolution has been mainly driven by a single large shift towards elongation in Tendiculophora, which contains the majority of described siphonophore species. There is one secondary return to more oval, less elongated haplonemes in *Erenna*, but it doesn't reach the sphericity present in Cystonectae or Pyrostephidae (Fig. \@ref(figure10)). Heteroneme evolution presents a less radical evolutionary history, where Tendiculophora evolved more elongate heteronemes, but the difference between theirs and other siphonophores is much smaller than the variation in shape within Tendiculophora, bearing no phylogenetic signal. In this group, the evolution of heteroneme shape has diverged in both directions, and there is no correlation with haploneme shape, which has remained fairly constant (elongation between 1.5 and 2.5).

@@

Data available from the Dryad Digital Repository: [http://dx.doi.org/10.5061/dryad.NNNN](http://dx.doi.org/10.5061/dryad.[NNNN])
Online Appendices are available in [https://github.com/dunnlab/tentilla_morph/Supplementary_materials/Online_Appendices](https://github.com/dunnlab/tentilla_morph/Supplementary_materials/Online_Appendices)

@@
